Safety and Liveness of Unmanned Aerial Vehicle Platoons on Air Highways

### 2016-05-13 docs/AIAA 2016 highway platooning/plat_sim.tex
A bit more proofreading

% !TEX root = main.tex
% 82 124 170 231
\subsection{Numerical Simulations}
In this section, we consider several situations that vehicles in a platoon on an air highway may commonly encounter, and show via simulations the behaviors that emerge from the controllers we defined in Sections \ref{sec:reach_ctrl} and \ref{sec:other_ctrl}.

>>>>

% !TEX root = main.tex
% 82 124 170 231
\subsection{Numerical Simulations}
In this section, we consider several situations that vehicles in a platoon on an air highway may commonly encounter, and show via simulations the behaviors that emerge from the controllers we defined in Sections \ref{sec:platooning}-\ref{sec:reach_ctrl} and \ref{sec:platooning}-\ref{sec:other_ctrl}.
